---
title: "Memory Curve"
author: "Hadrien Dykiel"
date: "8/23/2018"
output: html_document
references:
  - id: wikipedia
    title: artile-title
    URL: 'page-url'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(scales)
```

## Forgetting curve

The forgetting curve can be approximated with the following formula:

$$
R=e^{- \frac{t}{S}}
$$

$R$ is retrievability, a measure of how easy it is to retrieve a piece of information from memory. $S$ is stability of memory, which determines how fast $R$ falls over time in absence of training, testing, or other recall. $t$ represents time.

```{r}
# Simulate the Hermann Ebbinghaus Curve

# Recall 0
S <- 3 # original stickiness of memory (stability)
t <- c(0:30) # time in days

R <- sapply(t, function(x) exp(1)^(-x/S)) # calculate retrievability

df <- data.frame(t, R, recall.number = 0)


datalist = list()

for (i in seq(1,20,5)) {
    # ... make some data
    
    dat <- data.frame(days = t, retrievability = sapply(t + 1 - i,function(x) exp(1)^(-x/S)))
    dat$i <- i -1  # maybe you want to keep track of which iteration produced it?
    datalist[[i]] <- dat # add it to your list
    t <- t + 5
    S <- S + 5
}

big_data = do.call(rbind, datalist)
# or big_data <- dplyr::bind_rows(datalist)
# or big_data <- data.table::rbindlist(datalist)


# Plot graph
ggplot(data = big_data, aes(x = days, y = retrievability, color = i, group = i)) +
  scale_y_continuous(labels = scales::percent) +
  geom_line() +
  ggtitle(label = "The Forgetting Curve")


```

[ -@wikipedia]

Some useful links: 
[University of Warterloo: Curve of forgetting]("https://uwaterloo.ca/campus-wellness/curve-forgetting) 

## Spaced repitition

Several algorithms are available. The most simple is [Leitner's System]("https://en.wikipedia.org/wiki/Spaced_repetition")